WFH and broadband speed (title needs rework)

### 2020-11-24 paper/v1/broadband.speed.covid.Rmd
started working on the methods sectrion. haven't finished yet :(

Description of the method

>>>>

The core of the methodological framework of this paper lies upon clustering methods.
Clustering is a widely used family of techniques in geography (**ADD REF**),
which can be defined within the modern machine learning framework as an unsupervised
learning task, which involves partitioning unlabeled observations into homogeneous
groups known as clusters [@montero2014tsclust]. The key idea is that observations
within clusters tend to be more similar than observations between clusters.
Clustering is particularly useful for exploratory studies as it identifies
structures within the data [@aghabozorgi2015time].

Various applications of clustering can be found within geography: **ADD EXAMPLES**

Key characteristic of these studies is the cross-sectional nature of the data they
employed. Indeed, most clustering problems in geography deal with observations
that are fixed in time. However, for this paper we are interested in creating
clusters of local authorities in the UK with similar temporal signatures of
experienced internet speeds over time. Hence, we deviate from the established
geographical clustering tools and employ time series clustering methods.

Time series clustering methods have been developed in order to deal with clustering
problems linked to, for instance, stock or other financial data, economic,
governmental or medical data as well as machine monitoring
[@aggarwal2013time; @aggarwal2001surprising; @hyndman2015large; @WARRENLIAO20051857].
The main challenge -- and also the difference with cross-sectional clustering
problems -- is data dimensionality given the multiplicity of data points for every
individual included in the data set. Time series data are dynamic data as the
value of the observations change as a function of time [@aghabozorgi2015time].
This high dimensionality leads to (i) computational and algorithmic challenges
regarding handling these data and building algorithms to perform clustering over
long time series, and (ii) open questions regarding the choice of similarity
measures in order to cluster similar times series together considering the whole
length of the time series and overcoming issues around noise, outliers and shifts
[@lin2004iterative; @aghabozorgi2015time].

Time series clustering methods utilising the whole length of time series can be
grouped in three categories. The first -- model-based approaches -- is based on
recovering the underlying model for each time series and then apply clustering
algorithms on the model parameters [@aghabozorgi2015time]. The main criticism
is the cluster accuracy for near clusters [@mitsa2010temporal]. The second approach
is a based the formation of vectors of features based on the original time series.
These new data of reduced dimensionality is then clustered using conventional
clustering algorithms.

For this paper we utilise the third category of time series clustering methods
known as shape-based approaches. The main idea is to match any two sperate time
series based on the similarity of their shapes through the calculation of
distances among these two shapes.

@sardatime
Ideally, all members of the same cluster are similar to each other, but are as
dissimilar as possible from objects in a different cluster.

Time-series is a common type of dynamic data that naturally arises in many different scenarios,
such as stock data, medical data, and machine monitoring, just to name a few (Aghabozorgi et al.,
2015; Aggarwal and Reddy, 2013). They pose some challenging issues due to the large size and high
dimensionality commonly associated with time-series (Aghabozorgi et al., 2015). In this context,
dimensionality of a series is related to time, and it can be understood as the length of the series.

the data and how the underlying grouping is performed. One classification depends on whether the
whole series, a subsequence, or individual time points are to be clustered. On the other hand, the
clustering itself may be shape-based, feature-based, or model-based.

In the context of shape-based time-series clustering, it is common to utilize the Dynamic Time
Warping (DTW) distance as dissimilarity measure (Aghabozorgi et al., 2015). The calculation of the
DTW distance involves a dynamic programming algorithm that tries to find the optimum warping
path between two series under certain constraints

### 2020-11-24 paper/v1/broadband.speed.covid.tex
started working on the methods sectrion. haven't finished yet :(

Description of the method

>>>>

The core of the methodological framework of this paper lies upon
clustering methods. Clustering is a widely used family of techniques in
geography (\textbf{ADD REF}), which can be defined within the modern
machine learning framework as an unsupervised learning task, which
involves partitioning unlabeled observations into homogeneous groups
known as clusters \citep{montero2014tsclust}. The key idea is that
observations within clusters tend to be more similar than observations
between clusters. Clustering is particularly useful for exploratory
studies as it identifies structures within the data
\citep{aghabozorgi2015time}.

Various applications of clustering can be found within geography:
\textbf{ADD EXAMPLES}

Key characteristic of these studies is the cross-sectional nature of the
data they employed. Indeed, most clustering problems in geography deal
with observations that are fixed in time. However, for this paper we are
interested in creating clusters of local authorities in the UK with
similar temporal signatures of experienced internet speeds over time.
Hence, we deviate from the established geographical clustering tools and
employ time series clustering methods.

Time series clustering methods have been developed in order to deal with
clustering problems linked to, for instance, stock or other financial
data, economic, governmental or medical data as well as machine
monitoring
\citep{aggarwal2013time, aggarwal2001surprising, hyndman2015large, WARRENLIAO20051857}.
The main challenge -- and also the difference with cross-sectional
clustering problems -- is data dimensionality given the multiplicity of
data points for every individual included in the data set. Time series
data are dynamic data as the value of the observations change as a
function of time \citep{aghabozorgi2015time}. This high dimensionality
leads to (i) computational and algorithmic challenges regarding handling
these data and building algorithms to perform clustering over long time
series, and (ii) open questions regarding the choice of similarity
measures in order to cluster similar times series together considering
the whole length of the time series and overcoming issues around noise,
outliers and shifts \citep{lin2004iterative, aghabozorgi2015time}.

Time series clustering methods utilising the whole length of time series
can be grouped in three categories. The first -- model-based approaches
-- is based on recovering the underlying model for each time series and
then apply clustering algorithms on the model parameters
\citep{aghabozorgi2015time}. The main criticism is the cluster accuracy
for near clusters \citep{mitsa2010temporal}. The second approach is a
based the formation of vectors of features based on the original time
series. These new data of reduced dimensionality is then clustered using
conventional clustering algorithms.

For this paper we utilise the third category of time series clustering
methods known as shape-based approaches. The main idea is to match any
two sperate time series based on the similarity of their shapes through
the calculation of distances among these two shapes.

\citet{sardatime} Ideally, all members of the same cluster are similar
to each other, but are as dissimilar as possible from objects in a
different cluster.

Time-series is a common type of dynamic data that naturally arises in
many different scenarios, such as stock data, medical data, and machine
monitoring, just to name a few (Aghabozorgi et al., 2015; Aggarwal and
Reddy, 2013). They pose some challenging issues due to the large size
and high dimensionality commonly associated with time-series
(Aghabozorgi et al., 2015). In this context, dimensionality of a series
is related to time, and it can be understood as the length of the
series.

the data and how the underlying grouping is performed. One
classification depends on whether the whole series, a subsequence, or
individual time points are to be clustered. On the other hand, the
clustering itself may be shape-based, feature-based, or model-based.

In the context of shape-based time-series clustering, it is common to
utilize the Dynamic Time Warping (DTW) distance as dissimilarity measure
(Aghabozorgi et al., 2015). The calculation of the DTW distance involves
a dynamic programming algorithm that tries to find the optimum warping
path between two series under certain constraints
